International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-20 paper/4_app.tex
okay, good now
won't touch this again until new graphics are updated.  Table too!

\begin{figure}
\centering   
\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=65mm]{reiter_auc_outsamp.pdf}}
\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{reiter_pr_outsamp.pdf}}
\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}

@@

% TO DO: include discussion and analysis of different K's in appendix (for M cD)
\begin{figure}
\includegraphics[width=\textwidth]{McDonald_coefs.pdf}
\caption{\label{fig:mcdCoefs}Coefficient plot of McDonald (2004)'s original model (blue) compared to AME model (red).}
\end{figure}

%\begin{figure}
%\centering   
%\subfigure[AUC]{\label{fig:mcDauc}\includegraphics[width=65mm]{McDonald_auc_outsamp.pdf}}
%\subfigure[Precision and Recall]{\label{fig:mcDpr}\includegraphics[width=65mm]{McDonald_pr_outsamp.pdf}}
%\caption{\label{fig:mcdall} Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
%\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{rose_aeff_top10.pdf}
 \caption{Nodal Random Effects for AME estimation of Rose (2004).}\label{fig:roser}
\end{figure}

%\begin{figure}
%\centering   
%\subfigure[Nodal Random Effects]%{\label{fig:rosesend}\includegraphics[width=65mm]{ABplot_rose_top10.pdf}}
%\subfigure[Receiver Random Effects]{\label{fig:rosereceive}\includegraphics[width=65mm]{ABplot_receiver_rose.pdf}}
%\caption{Sender and receiver random effects for AME estimation of Rose (2004).}
%\label{fig:rosesr}
%\end{figure}

@@

The re-estimation of \citet{weeks:2012} likely has the sharpest divergence between the General Linear Model results and those of the AME Model. In Weeks's initial models,  she finds that machines are less prone to initiate conflict than the reference category, whereas Juntas, Bosses and Strong-men are more conflict-prone, in line with her theoretical expectations. When we look at the posterior distribution of these coefficients in the AME results, we find that none of these values are distinguishable from zero. We similarly find less pronounced effects for military capabilities. One explanation for this divergence is the AME model's ability to account for third order effects. Inspection of the multiplicative effects in Figure~\ref{fig:weekscirc} reveals a number of clusters of states which exhibit structural equivalence -- in the top right corner we see states like the US, the UK, and Israel who often send conflict to similar targets. In particular, we observe a cluster of ``rogue states,'' who are receivers of conflict, in the top right (Iran, Iraq, Syria, Libya, North Korea). In the bottom corner we see a cluster of authoritarian senders including Iraq, Russia, Syria, North Korea and China. In general, these clusters have similar governmental types (Iraq, Syria, Libya, and North Korea all fell under the ``boss" category), and similar conflict behavior. So, in the GLM, which ignores these third order dependencies, much of these results might have been attributed to regime type. The AME model, on the other hand, finds that it is more efficient to attribute this behavior to the multiplicative effects. In terms of out of sample performance, shown in Figure~\ref{fig:weeksauc}, the AME model performs markedly better than the GLM out of sample, lending credence to the possibility that these third order dependencies cause spurious effects for regime type.

\begin{figure}
	\includegraphics[width=\textwidth]{weeks_coefs_all.pdf}
	\caption{\label{fig:weeksCoef} Coefficient plot of Weeks' (2012) original model (blue) compared to AME model (red). }
\end{figure}

\begin{figure}
\centering   
	\subfigure[AUC]{\label{fig:weeksauc}\includegraphics[width=65mm]{weeks_auc_outsamp.pdf}}
	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{weeks_pr_outsamp.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Weeks (2012) using ROC curves and PR curves.}
\end{figure}

\begin{figure}
	\includegraphics[width=\textwidth]{weeks_circPlot.pdf}
	\caption{\label{fig:weekscirc} Visualization of multiplicative effects for Weeks (2012). Blue represents groups with common sending patterns and red represents groups with common receiving patterns.}
\end{figure}

>>>>

\begin{figure}
\centering   
\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=65mm]{reiter_auc_outsamp.pdf}}
\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{reiter_pr_outsamp.pdf}}
\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

@@

% TO DO: include discussion and analysis of different K's in appendix (for M cD)
\begin{figure}
\includegraphics[width=\textwidth]{McDonald_coefs.pdf}
\caption{\label{fig:mcdCoefs}Coefficient plot of McDonald (2004)'s original model (blue) compared to AME model (red).}
\end{figure}
\FloatBarrier
%\begin{figure}
%\centering   
%\subfigure[AUC]{\label{fig:mcDauc}\includegraphics[width=65mm]{McDonald_auc_outsamp.pdf}}
%\subfigure[Precision and Recall]{\label{fig:mcDpr}\includegraphics[width=65mm]{McDonald_pr_outsamp.pdf}}
%\caption{\label{fig:mcdall} Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
%\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{rose_aeff_top10.pdf}
 \caption{Nodal Random Effects for AME estimation of Rose (2004)}\label{fig:roser}
\end{figure}
\FloatBarrier
%\begin{figure}
%\centering   
%\subfigure[Nodal Random Effects]%{\label{fig:rosesend}\includegraphics[width=65mm]{ABplot_rose_top10.pdf}}
%\subfigure[Receiver Random Effects]{\label{fig:rosereceive}\includegraphics[width=65mm]{ABplot_receiver_rose.pdf}}
%\caption{Sender and receiver random effects for AME estimation of Rose (2004).}
%\label{fig:rosesr}
%\end{figure}

@@

The re-estimation of \citet{weeks:2012} likely has the sharpest divergence between the General Linear Model results and those of the AME Model. In Weeks's initial models,  she finds that machines are less prone to initiate conflict than the reference category, whereas Juntas, Bosses and Strong-men are more conflict-prone, in line with her theoretical expectations. When we look at the posterior distribution of these coefficients in the AME results, we find that none of these values are distinguishable from zero. We similarly find less pronounced effects for military capabilities. One explanation for this divergence is the AME model's ability to account for third order effects. Inspection of the multiplicative effects in Figure~\ref{fig:weekscirc} reveals a number of clusters of states which exhibit structural equivalence -- in the top right corner we see states like the US, the UK, and Israel who often send conflict to similar targets. In particular, we observe a cluster of ``rogue states,'' who are receivers of conflict, in the top right (Iran, Iraq, Syria, Libya, North Korea). In the bottom corner we see a cluster of authoritarian senders including Iraq, Russia, Syria, North Korea and China. In general, these clusters have similar governmental types (Iraq, Syria, Libya, and North Korea all fell under the ``boss" category), and similar conflict behavior. So, in the GLM, which ignores these third order dependencies, much of these results might have been attributed to regime type. The AME model, on the other hand, finds that it is more efficient to attribute this behavior to the multiplicative effects. In terms of out-of-sample performance, shown in Figure~\ref{fig:weeksauc}, the AME model performs markedly better than the GLM out of sample, lending credence to the possibility that these third order dependencies cause spurious effects for regime type.

%. THINK THIS IS GONE 
%\begin{figure}
%	\includegraphics[width=\textwidth]{weeks_coefs_all.pdf}
%	\caption{\label{fig:weeksCoef} Coefficient plot of Weeks' (2012) original model (blue) compared to AME model (red). }
%\end{figure}
\begin{figure}
	\includegraphics[width=\textwidth]{weeks_circPlot.pdf}
	\caption{\label{fig:weekscirc} Visualization of multiplicative effects for Weeks (2012). Blue represents groups with common sending patterns and red represents groups with common receiving patterns.}
\end{figure}

\begin{figure}
\centering   
	\subfigure[AUC]{\label{fig:weeksauc}\includegraphics[width=65mm]{weeks_auc_outsamp.pdf}}
	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{weeks_pr_outsamp.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Weeks (2012) using ROC curves and PR curves}
\end{figure}
